\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
Specifications:

\begin{itemize}
  \item 1. The lockout/tagout panel shall be used.

  \begin{todolist}
    \item The lockout/tagout panel was installed in the hasp and locked during all work on the rack
  \end{todolist}

  \item 2. Power shall be provided to the control circuits via appropriate PLC outputs.
  \begin{todolist}
    \item The button and lights were both provided with power from 120VAC PLC output terminals.
    \end{todolist}

  \item 3. The PLC shall be powered by a 120 VAC source.
  \begin{todolist}
      \item The PLC receives power from a 120VAC outlet in the wall.
  \end{todolist}
  \item 4. Power to the PLC shall be protected by a lock-out/tag-out mechanism.
  \begin{todolist}
      
      \item The button that energizes the PLC and associated equipment is protected by a locking hasp.
  \end{todolist}

    \item 5. The PLC shall be protected on the 120 VAC side by an appropriately-rated fuse.
  \begin{todolist}
      \item A fuse rated for 1.5A based on the specification of the PLC is installed inline with the power to the PLC.
  \end{todolist}

      \item 6.The design shall be implemented using a DL205 PLC.
  \begin{todolist}
      \item The DL205 PLC is the basis of our design.
  \end{todolist}
  
      \item 7. The design shall be implemented using the Do-More Designer Software suite.
  \begin{todolist}
      \item Programming of the DL205 was achieved via Do-More Designer.
  \end{todolist}
  
      \item 8. All components shall be mounted on a panel.
  \begin{todolist}
      \item The components are mounted on panels in a 19 inch rack.
  \end{todolist}
  
      \item 9. Strain reliefs or rubber grommets shall be used for all panel thru-holes.
  \begin{todolist}
      \item All cables are protected upon passing through the rack via a rubber grommet.
  \end{todolist}
  
      \item 10. Appropriate and consistent color coding shall be used for all conductors and terminal blocks.
  \begin{todolist}
      \item All lines leading from a power source to an input are red in color. All lines connected between an output and a PLC terminal are white in color, as is the neutral connector into our power supply. All ground cables are green and connected to green connector blocks.
  \end{todolist}
  
      \item 11. The following items shall be mounted on the panel:
• A green 22 mm pilot 
• A red 22 mm pilot 
• A blue 22 mm momentary button 

  \begin{todolist}
      \item Our panel features all three of these items.
  \end{todolist}
  
      \item 12. The green pilot light shall turn on when the circuit is first energized.
  \begin{todolist}
      \item The green light is illuminated by default upon energizing the panel.
  \end{todolist}


      \item 14. The red pilot light shall turn on when the blue momentary button is depressed if the green pilot light is on.
  \begin{todolist}
      \item We programmed this behavior with Do-More into the PLC and it works as described.
  \end{todolist}
  
  \item 15. The red pilot shall remain on after the blue momentary button is released.
  \begin{todolist}
      \item We programmed this behavior with Do-More into the PLC and it works as described.
  \end{todolist}
  
  \item 16. The green pilot light shall turn on when the blue momentary button is depressed if the red pilot light is on.
  \begin{todolist}
      \item We programmed this behavior with Do-More into the PLC and it works as described.
  \end{todolist}
  
  \item 17. The green pilot shall remain on after the blue momentary button is released.
  \begin{todolist}
      \item We programmed this behavior with Do-More into the PLC and it works as described.
  \end{todolist}
  
\end{itemize}